Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-29 edubots_surveys.Rnw
Adapt @noorhanabbas incorporation

Given the potential benefits that chatbots could bring to the classroom, the
focus of the
% EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
{\sf anonymized European Project}, the sponsor of this study, is to
\textcolor{blue}{explore best practices and innovative use of chatbots, and to create 
a learning community of educators in higher education institutions.
The majority of studies conducted so far have studied how these 
messaging applications and/or chatbots are used to deliver personalised
learning in classrooms that occurs anytime anywhere, 
promote collaborative learning experiences, group discussions \cite{panah2020study}
and for boosting students' sense of belonging to their 
institutions \cite{abbas2021onlinechat}. Hence, due to the paucity of research
that explores the use of these technologies from the teachers' perspectives,
this paper aims to investigate their opinions/needs and the
challenges/opportunities of adopting these technologies in classrooms
to paint a better picture of how they can positively contribute to enhancing
the learning process in higher education institutions.}

>>>>

Given the potential benefits that chatbots could bring to the classroom, the
focus of the
% EDUBOTS KA2 European project \footnote{https://www.edubots.eu},
{\sf anonymized European Project}, the sponsor of this study, is to
\textcolor{blue}{explore best practices and innovative use of chatbots, and to create 
a learning community of educators in higher education institutions.
The majority of studies conducted so far have studied how these 
messaging applications and/or chatbots are used to deliver personalised
learning in classrooms that occurs anytime anywhere,
promote collaborative learning experiences, group discussions \cite{panah2020study}
and boost students' sense of belonging to their institutions
\cite{abbas2021onlinechat}. Hence, due to the paucity of research
that explores the use of these technologies from the teachers' perspectives,
this paper aims to investigate their opinions/needs and the
challenges/opportunities of adopting these technologies in classrooms
to paint a better picture of how they can positively contribute to enhancing
the learning process in higher education institutions.}
